Causal Inference with Graphical Neural Networks

### 2024-04-10 latex/draft.tex
Pushing some fun latex changes.

\title{Causal Inference with Graphical Neural Networks}
\author{Your Name}
\date{\today}
\maketitle

@@

@@

For our project, we used the LUCAS0 dataset~\cite{lucas_dataset}, which is a toy data set 
generated artificially by causal Bayesian networks with binary variables. The LUCAS0 dataset
is a DAG with 11 nodes and 2000 training samples, where the DAG is represented as

\begin{figure}[h]
    \centering
    \begin{tikzpicture}[scale=1.5, Bullet/.style={circle, draw=black, fill=#1, inner sep=0pt, minimum size=3mm, line width=1.pt}]
        \draw[help lines, gray] (0,0) grid (6,6);
        \node[ellipse, draw=black, fill=lime] (A) at (2,2){Anxiety};
        \node[ellipse, draw=black, fill=lime, align=center] (P) at (4,2){Peer\\Pressure};
        \node[ellipse, draw=black, fill=teal] (S) at (3,1){Smoking};
        \node[ellipse, draw=black, fill=lime, align=center] (Y) at (1,1){Yellow\\Fingers};
        \node[ellipse, draw=black, fill=lightgray, align=center] (B) at (6, 2){Born on\\Even Day};
        \node[ellipse, draw=black, fill=teal, align=center] (G) at (5, 1){Genetics};
        \node[ellipse, draw=black, fill=teal, align=center] (C) at (2, 0){Allergy};
        \node[Bullet=cyan,label=below :{$X$}] (X) at (0,0){};

        \draw[->, line width=1] (A) -- (S);
        \draw[->, line width=1] (P) -- (S);
        \draw[->, line width=1] (S) -- (Y);

    \end{tikzpicture}
    \caption{Basic causal diagram. Note it is in the form of a directed acyclic graph (DAG).}
    \label{fig:lucas_dag}
\end{figure}

@@

% Bibliography
\bibliographystyle{plain}
\bibliography{references} % Replace 'references' with the name of your .bib file

>>>>

\title{Causal Inference with Graphical Neural Networks}
\author{Gwen Johnson\and Dylan Skinner\and Dallin Stewart\and Jason Vasquez}
\date{\today}
\maketitle

@@

\section{Graph Neural Networks}

Originally proposed in 2005 by Mori et al.~\cite{gori2005new}, Graph Neural Networks 
(GNNs) are a class of neural networks that operate on graph-structured data. 
They have gained significant attention in recent years due to their versatility 
in handling various types of graph data, including social networks, citation networks, 
biological networks, and more.

Unlike traditional neural networks, which operate on 
grid-like structures such as images or sequences, GNNs are specifically designed to 
capture and leverage the structural information present in graphs. One of their 
key strengths lies in their ability to learn meaningful representations of nodes in a 
graph, which can then be used for various downstream tasks such as node classification, 
link prediction, and graph classification. Their ability to capture and model complex 
relationships in graph data makes them invaluable tools for exploring and understanding 
real-world phenomena represented in graph form.

In our project, we are utilizing the power of GNNs to perform a supervised classification
task. This means we are training a GNN on a labeled, tabular dataset, where each graph instance
(or node) is associated with a target label.

@@

For our project, we used the LUCAS0 dataset~\cite{lucas_dataset}, which is a toy data set 
generated artificially by causal Bayesian networks with binary variables. The LUCAS0 dataset
is a DAG with 11 nodes and 2000 training samples, where the DAG is represented as in Figure~\ref{fig:lucas_dag}.

\begin{figure}[h]
    \centering
    \begin{tikzpicture}[scale=1.5, Bullet/.style={circle, draw=black, fill=#1, inner sep=0pt, minimum size=3mm, line width=1.pt}]
        % \draw[help lines, gray] (0,0) grid (6,6);
        \node[ellipse, draw=black, fill=lime] (A) at (2,2){Anxiety};
        \node[ellipse, draw=black, fill=lime, align=center] (P) at (4,2){Peer\\Pressure};
        \node[ellipse, draw=black, fill=teal] (S) at (3,1){Smoking};
        \node[ellipse, draw=black, fill=lime, align=center] (Y) at (1,1){Yellow\\Fingers};
        \node[ellipse, draw=black, fill=lightgray, align=center] (B) at (6, 2){Born on\\Even Day};
        \node[ellipse, draw=black, fill=teal, align=center] (G) at (5, 1){Genetics};
        \node[ellipse, draw=black, fill=teal, align=center] (Al) at (2, 0){Allergy};
        \node[ellipse, draw=black, fill=pink, align=center] (L) at (4, 0){Lung\\Cancer};
        \node[ellipse, draw=black, fill=lime, align=center] (AD) at (6, 0){Attention\\Disorder};
        \node[ellipse, draw=black, fill=teal, align=center] (C) at (3, -1){Coughing};
        \node[ellipse, draw=black, fill=teal, align=center] (F) at (5, -1){Fatigue};
        \node[ellipse, draw=black, fill=lime, align=center] (CA) at (6, -2){Car\\Accident};

        \draw[->, line width=1] (A) -- (S);
        \draw[->, line width=1] (P) -- (S);
        \draw[->, line width=1] (S) -- (Y);
        \draw[->, line width=1] (S) -- (L);
        \draw[->, line width=1] (G) -- (L);
        \draw[->, line width=1] (G) -- (AD);
        \draw[->, line width=1] (Al) -- (C);
        \draw[->, line width=1] (L) -- (C);
        \draw[->, line width=1] (L) -- (F);
        \draw[->, line width=1] (C) -- (F);
        \draw[->, line width=1] (F) -- (CA);
        \draw[->, line width=1] (AD) -- (CA);

    \end{tikzpicture}
    \caption{Basic causal diagram. Note it is in the form of a directed acyclic graph (DAG). Our target variable
    is shaded in ${\color{pink} \textbf{pink}}$, and the nodes in {\color{teal} \textbf{teal}} constitude the Markov
    blanket of the target variable.}
    \label{fig:lucas_dag}
\end{figure}

@@

\newpage
% Bibliography
\bibliographystyle{plain}
\bibliography{references} % Replace 'references' with the name of your .bib file
